---
title: "A Simple Example: Multilevel Manifest AR(1) Model"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{manifest_ar_example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(mlts)
```

One of the simplest models we can fit with `mlts` is a first order autoregressive model with only one observed variable. We start by specifying the model with `mlts_model()`. The argument `q` controls the number of time-series constructs. For this simple model, the following call is sufficient:

```{r}
ar1_model <- mlts_model(q = 1)
```

We can check the parameters present in the model by just calling the object:

```{r}
ar1_model
```

When `mlts_model()` sets up this model, all model parameters are free (i.e., not constrained) by default. In the AR(1) model, there are three fixed effects: the grand mean (`mu_1`) of the outcome, the autoregressive effect (`phi(1)_11`), and the innovation variance (`ln.sigma2_1`).
